### 2015-04-17 bugfinding.tex
Working on the Corral section.

\whoop is a sound but potentially imprecise static data race analyser. In our experience, developers appreciate soundness but do not want to get overwhelmed by countless false positive reports. Towards this we allow an external precise bug-finder to be plugged in the \whoop infrastructure. The race-related information generated by \whoop can then be used to accelerate the bug-finder a bug-finder for concurrent programs that can be easily plugged in our infrastructure. Currently we only support \corral~\cite{lal2012corral}, a state-of-the-art bug-finder used in Microsoft to analyse Windows device drivers. We chose \corral because it is open-source and because it accepts Boogie IVL, similar to \whoop. Our technique, though, should be able to accelerate any arbitrary bug-finder for concurrent programs.

@@

\corral is a verifier for Boogie IVL that uses SMT solvers (e.g. Z3 or CVC4) underneath to reason about program behaviour and reports a counterexample if an assertion violation is found. \corral attempts to prove reachability of a bug in a goal-directed, lazy fashion to postpone state space explosion when analysing a complex concurrent program. Towards this, \corral performs two abstractions: (i) variable abstraction, where it attempts to identify a minimal set of shared variables that impact the generated verification conditions; and (ii) stratified inlining, where it attempts to identify a minimal unrolling of loops and recursion that also impact the generated verification conditions.

Because \corral performs bounded model checking, it is inherently unsound, in other words it can miss real bugs. Assuming a precise environmental model, though, \corral will only report true bugs. \whoop takes advantage of this precision to report only feasible data races.

>>>>

\whoop is a sound but potentially imprecise static data race analyser.  While
developers do appreciate soundness, it is more important to ensure they are not
overwhelmed by countless reports of false bugs.  Hence, to improve precision, we
enable an external precise bug-finder for concurrent programs to be plugged into
the \whoop infrastructure. The race-related information generated by \whoop can
then be used to accelerate the bug-finder.  Currently, we support
\corral~\cite{lal2012corral}, a state-of-the-art scalable bug-finder used by
Microsoft to analyse Windows device drivers. \corral accepts Boogie IVL and
hence it was easy to integerate into our tool flow. Our technique, though, is
general and capable of accelerating any arbitrary bug-finder for concurrent
programs.

@@

\corral is a symbolic bounded verifier for Boogie IVL that uses SMT solvers
(e.g., Z3 or CVC4) to statically reason about program behaviours. It checks for
violations of provided assertions, and reports a precise counterexample if an
assertion violation is found. \corral performs bounded exploration of a
concurrent program in two steps. First, given a bound on the number of allowed
context-switches, the concurrent program is appropriately \emph{sequentialized},
and the generated sequential version preserves reachable states of the original
concurrent program~\cite{popl2011-eqr,cav2009-lqr,cavLalR08}.  Then, \corral
attempts to prove bounded (in terms of the number of loop iterations and
recursion depth) sequential reachability of a bug in a goal-directed, lazy
fashion to postpone state space explosion when analysing a large program.  It
performs two abstractions to achieve this: (i) variable abstraction, where it
attempts to identify a minimal set of shared variables that have to be precisely
tracked in order to discharge all assertions; and (ii) stratified inlining,
where it attempts to inline procedures on-demand as they are required for
proving program assertions.

Because \corral performs bounded verification both in terms of the number of
allowed context switches and loop/recursion unrollings, it is inherently
unsound; in other words, it can miss real bugs. On the other hand, \corral is
precise, and assuming a precise model of the program environment it will only
report true bugs. \whoop takes advantage of this precision to report only
feasible data races.
